Housing mice Notebook

### 2022-06-29 minos/transitions/housing/housing_mice.Rmd
add mwb framework. need to get ols model working now.

```{r}
source("utils.R") # for data formatting functions and other useful globals. 
require(VIM) # for missingness visualisation.
require(mice) # for mice multiple imputation.
require(lattice) # for mice imputation functions.
require(ordinal) # for clm models.
require(tidyr) # for data frame formatting.
require(viridis) # for python's nice colour palettes

@@

```{r}
imp_columns <- c("five_household", "heating", "labour_state", "education_state",
                 "sex", "job_sec", "ethnicity", "age", "SF.12")
house_mice <- mice(data = data[,imp_columns],
                 m = 20, maxit = 20, seed = 500,
                 remove.collinear=T)
```

@@

```{r}
data2<- complete(house_mice)
data2 <- tidyr::drop_na(data2)
# format final housing composite. If they have no appliances assign 0.
# any up to 5 assign 1.
# all assign 2.
data2$housing <- rowSums(data2[, c("five_household", "heating")])
data2[which(data2$housing <= 3), "housing"] <- 0
data2[which(data2$housing <= 4 & data2$housing > 3), "housing"] <- 1
data2[which(data2$housing >= 5), "housing"] <- 2

@@

formula <- "housing ~ factor(sex) + 
                      age + 
                      SF.12 + 
                      factor(labour_state) +
                      factor(job_sec)"
housing.clmm <- clm(housing ~ factor(sex) + 
                                age + 
                                SF.12 + 
                                factor(labour_state) +
                                factor(job_sec) +
                                factor(ethnicity), 
                                data= train[complete.cases(train),],
                                link = "logit",
                                threshold = "flexible",
                                Hess=T)

@@

>>>>

```{r}
source("utils.R") # for data formatting functions and other useful globals. 
require(VIM) # for missingness visualisation.
require(mice) # for mice multiple imputation.
require(lattice) # for mice imputation functions.
require(ordinal) # for clm models.
require(tidyr) # for data frame formatting.
require(viridis) # for python's nice colour palettes
require(ggplot2) # for confusion matrix plots
#require(dplyr) # matrix manipulation
require(stringr)# for fancy wrapped text in confusion matrix axis labels
require(shadowtext) #^

@@

```{r}
imp_columns <- c("five_household", "heating", "labour_state", "education_state",
                 "sex", "job_sec", "ethnicity", "age", "SF.12", "hh_netinc")
house_mice <- mice(data = data[, imp_columns],
                 m = 10, maxit = 10, seed = 500,
                 remove.collinear=T)
```

@@

```{r}
data2<- complete(house_mice)
data2 <- tidyr::drop_na(data2)
# format final housing composite. If they have no appliances assign 0.
# any up to 5 assign 1.
# all assign 2.
data2$housing <- rowSums(data2[, c("five_household", "heating")])
data2[which(data2$housing <= 0), "housing"] <- 0
data2[which(data2$housing <= 5 & data2$housing > 1), "housing"] <- 1
data2[which(data2$housing >= 6), "housing"] <- 2

@@

formula <- "housing ~ factor(sex) + 
                      age + 
                      SF.12 + 
                      factor(labour_state) +
                      factor(job_sec)"
housing.clmm <- clm(housing ~ (factor(sex) + 
                                factor(education_state) + 
                                age + 
                                SF.12 + 
                                factor(labour_state) +
                                factor(job_sec) +
                                factor(ethnicity) + hh_netinc)**2, 
                                data= train[complete.cases(train),],
                                link = "logit",
                                threshold = "flexible",
                                Hess=T)

@@

```{r}
confusion.matrix<- table(y, predict(housing.clmm, test, type="class")$fit)
group_pops<-rowSums(confusion.matrix)
confusion.frame <- as.data.frame(confusion.matrix/group_pops) # convert to data frame
confusion.frame$Freq <-round(confusion.frame$Freq, 3) # round to 2dp
row_names <- paste0(rownames(confusion.matrix), " [")
row_names <- paste0(row_names,  as.character(group_pops))
row_names <- paste0(row_names, "]")
row_names <- str_wrap(row_names, width = 12)
col_names <- str_wrap(colnames(confusion.matrix), 10)

confusion.plot<- ggplot(confusion.frame, aes(Var2, rev(y), fill= Freq)) +
  scale_fill_viridis_c("% of state")+
  geom_tile() + 
  geom_shadowtext(aes(label=Freq)) +
  #scale_fill_gradient(high="#87ceeb", low="#e34234") +
  labs(y = "True State [population in state]",x = "Predicted State (no units)") + 
  scale_y_discrete(labels=rev(row_names)) + # label axes
  scale_x_discrete(labels=col_names)
print(confusion.plot)
```
